Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

  # Add confidence intervals and p-values
  pooled_ame <- pooled_ame |>
    mutate(
      CI_Lower = AME - 1.96 * SE,
      CI_Upper = AME + 1.96 * SE,
      Z_stat = AME / SE,
      P_Value = 2 * pnorm(-abs(Z_stat))
    ) |>
    select(-Z_stat)

>>>>

  # Add confidence intervals and p-values
  pooled_ame <- pooled_ame |>
    mutate(
      CI_Lower = AME - 1.96 * SE,
      CI_Upper = AME + 1.96 * SE,
      P_Value = 2 * pnorm(-abs(AME / SE))
    )
